### 2014-11-11 tex/bisimulation.tex
Fixed some typoes

\section{Bisimularity Relation}
Let $p \rgse p^\prime$ be the binary relation over the universe of states, $S$,
according to generalized symbolic execution with lazy initialization
(see the supplemental text for a precise definition of that
relation). Similarly, let $q \rsym q^\prime$ be the relation for the GSESH
algorithm in this paper. The principle theoretical result is the
existence of a bisimularity relation between states related on $p \rgse p^\prime$
and the states related on $q \rsym ^\prime$. A corollary is that $\rsym$ is
both sound and complete with respect to $\rgse$. Only a summary of the
proof is given due to space.

The inspiration for $\rsym$ came from a desire to create
a new way to initialize heap objects that avoided initializing heaps
that traverse redundant paths. The thought was to group together heaps
into equivalence classes: all the heaps that followed the same control
flow path to a given point of execution would be in the same
equivalence class at that point of execution. An equivalence class
splits at branches, where the program actually differentiates heaps.

@@

Let $p \rgse p^\prime$ be defined as a union over state relations:
$$
\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A\cdot} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W\cdot} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E\cdot} \cup \rgse^\com
$$
where \emph{A} is a field access $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
\rightarrow \cfgnt{k}\rp$, \emph{W} is a field write $\lp
\cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare $\lp
\cfgnt{v}\ \cfgt{=}\ \cfgnt{*} \rightarrow \cfgnt{k}\rp$, $\cdot$
indicates a null reference in the operation or a false outcome, and
\emph{\com} is everything else in the language. A state relation is trivially extended to sets of states as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
Let $\rgse$ be the extension of $\rgse$ to sets of states.
$$
\rsgse = \rgse^\mathit{A}
\cup \rgse^\mathit{A\cdot} \cup \rgse^\mathit{W} \cup
\rgse^\mathit{W\cdot} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E\cdot}
\cup \rgse^\com
$$
The definition embodies the notion of splitting equivalence classes at
certain operations. The set $P$ at a field access for example has two
potential successors: a non-null and null reference. Respectively, the
set $P \rgse^\com$ only has a single successor since those expressions
are not related to control flow.

>>>>

\section{Bisimularity Relation}
Let $p \rgse p^\prime$ be the binary relation over the universe of states, $S$,
according to generalized symbolic execution with lazy initialization
(see the supplemental text for a precise definition of that
relation). Similarly, let $q \rsym q^\prime$ be the relation for the GSESH
algorithm in this paper. The principle theoretical result is the
existence of a bisimularity relation between states related on $p \rgse p^\prime$
and the states related on $q \rsym q^\prime$. A corollary is that $\rsym$ is
both sound and complete with respect to $\rgse$. Only a summary of the
proof is given due to space.

The inspiration for $\rsym$ came from a desire to create
a new way to initialize heap objects that avoided initializing heaps
that traverse the same control flow paths. The thought was to group together heaps
into equivalence classes: all the heaps that followed the same control
flow path to a given point of execution would be in the same
equivalence class at that point of execution. An equivalence class
splits at branches, where the program actually differentiates heaps.

@@

Let $p \rgse p^\prime$ be defined as a union over state relations:
$$
\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A\cdot} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W\cdot} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E\cdot} \cup \rgse^\com
$$
where \emph{A} is a field access $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
\rightarrow \cfgnt{k}\rp$, \emph{W} is a field write $\lp
\cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare $\lp
\cfgnt{v}\ \cfgt{=}\ \cfgnt{*} \rightarrow \cfgnt{k}\rp$, $\cdot$
indicates a null reference in the operation or a false outcome, and
\emph{\com} is everything else in the language. Any state relation, say $\rightarrow_x$, is trivially extended to sets of states as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
Let $\rgse$ be the extension of $\rgse$ to sets of states.
$$
\rsgse = \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A\cdot} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W\cdot} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E\cdot}
\cup \hookrightarrow_\gse^\com
$$
The definition embodies the notion of splitting equivalence classes at
certain operations. The set $P$ at a field access for example has two
potential successors: a non-null and null reference. Respectively, the
set $P \rgse^\com$ only has a single successor since those expressions
are not related to control flow.
